For_Clark

### 2020-07-16 Rcode/For_Clark.Rmd
update2

New data mean in Parks 
L71 will need to be hashed out when working with full data - it selects only the months which have data in our sample folder
L93 values need to change based on the length of your new filepath
```{r}

>>>>

Mean in Parks w/ New Data
L71 will need to be hashed out when working with full data - it selects only the months which have data in our sample folder
L93 values need to change based on the length of your new filepath
```{r}
